\documentclass[11pt, a4paper]{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=blue
}

\title{Gesnhin Impact total Wish approximation}
\author{Author: d4vidyo\footnotemark[1]}
\date{Date: September 2023}

\footnotetext[1]{Email: \texttt{d4vidyo@gmail.com}}\\
\begin{document}

\maketitle
\vfill
\begin{abstract}
This paper examines the Masterless Starglitter System in Genshin Impact (miHoYo, 2020) from the perspective of a player reinvesting their Wish-earned Glitter into new Wishes. The goal is to calculate the total number of Wishes a player can make starting with a certain amount of Primogems/Wishes.
\\
To simplify the calculations for players, certain assumptions are made. Through a systematic mathematical analysis, we derive a general formula.
\\
\\
\end{abstract}
\newpage

\tableofcontents
\newpage


\section{Introduction}

\subsection{Rules}
As stated in the Genshin Impact Wish details, the relevant rules for a Character Banner are as follows:
\begin{enumerate}
    \item \textbf{4-Star:}
    \begin{enumerate}
        \item A player is guaranteed a 4-Star or above item at least once per 10 attempts.
        \item A 4-Star weapon will always also give 2 Masterless Starglitter.
        \item A 4-Star character will also give 2 Masterless Starglitter if the player already owns this character. From the 8th copy onwards, 5 Masterless Starglitter are given instead.
    \end{enumerate}

    \item \textbf{5-Star:}
    \begin{enumerate}
        \item A player is guaranteed a 5-Star character at least once per 90 attempts.
        \item The Character Banner does not give any 5-Star weapons.
        \item A 5-Star character will also give 10 Masterless Starglitter if the player already owns this character. From the 8th copy onwards, 25 Masterless Starglitter are given instead.
    \end{enumerate}
\end{enumerate}
In the Paimon's Bargain item shop, we can exchange 5 Masterless Starglitter for 1 Intertwined Fate.


\subsection{Assumptions}
\begin{enumerate}
    \item Exactly every 10th pull is a 4-Star.
    \item Every 4-Star pull gives 2 Masterless Starglitter.
\end{enumerate}
\subsection{Assumption induced errors}
\begin{enumerate}
\item A 4-Star can be pulled more frequently than only on every 10th pull.
\item A 4-Star only gives Masterless Starglitter if duplicate or weapon.
\item A 4-Star can give 5 Masterless Starglitter if constellations are at max.
\item 5-Star pulls are not taken into account 
\end{enumerate}
\newpage

\section{Calculations}
\subsection{Naming Conventions}
$W_T:=$ Total Wish amount. (Number in Question)\\
$P_0:=$ Raw Primogems available.\\
$W_0:=$ Raw Intertwined Fate available.\\
$e_0:=$ Extra Wishes after spending $P_0$ Primogems.\\
$e_1:=$ Extra Wishes after spending $e_0$ Wishes.\\
$E:=(e_n)_{n \in \mathbb{N}}$ Sequenz of Extra Wishes. $e_0, e_1,...$ \\
\\

\subsection{Calculations}
The Total Wish amount $W_T$ should be calculated as:
$$W_T:=\frac{P_0}{160}+\sum_{n=0}^{N}e_n$$
The first Element $e_0$ of $E$ is calculated with:
$$e_0:=\frac{P_0}{160}\cdot\frac{1}{10}\cdot2\cdot\frac{1}{5}=\frac{P_0}{4.000}$$
$\frac{P_0}{160}$ gives us the amount of Wishes available at the start with $P_0$ Primogems. We divide it by $10$ to get the amount of 4-Star pulls. We multiply this by $2$ because each 4-Star pull gives $2$ Masterless Starglitter. We divide this by $5$ because we need 5 Masterless Starglitter to buy another Wish.
\\
The following Elements $e_n$ of $E$ are defined recursively with:
$$e_n:=e_{n-1}\cdot\frac{1}{10}\cdot2\cdot\frac{1}{5}= \frac{e_{n-1}}{25}$$
$e_{n-1}$ does not need to be divided by $160$ because it already is a Wish number rather than a Primogem number.
\\
We can express the $n$-th Element of $E$ as:
$$e_n=e_0\cdot\frac{1}{25^n}= \frac{P_0}{4.000}\cdot\frac{1}{25^{n}}$$
\\
Therefore the Total Wish amount can be expressed as:
$$W_T=\frac{P_0}{160}+\frac{P_0}{4.000}\cdot\sum_{n=0}^{N}\frac{1}{25^n}$$
Which contains a Geometric series and can therefore be written as:
$$W_T =\frac{P_0}{160}+\frac{P_0}{4.000}\cdot\frac{1-(\frac{1}{25})^{N+1}}{1-(\frac{1}{25})}$$
We can easily calculate a Limit of this function
$$\lim_{N\to\infty}\frac{1-(\frac{1}{25})^{N+1}}{1-(\frac{1}{25})}=\frac{1-0}{1-(\frac{1}{25})} = \frac{25}{24}$$
Which now gives us our final approximation of our Total Wishes
\begin{center}
$W_T=\frac{P_0}{160}+\frac{P_0}{4.000}\cdot\frac{25}{24}$
\end{center}
\\
\begin{center}
$W_T=\frac{P_0}{160}+\frac{P_0}{3840}$
\end{center}
\newpage

\section{Summary}
As seen in the Assumption section above this is not an accurate formula and doesnt take some unknown factors into account. But due to its simplicity it can give a quick and easy overview of the to expected Total Wishes.
The Formula gets even simpler when using our Intertwined Fate count $W_0$ instead of our Primogem count $P_0$:
$$W_T = W_0 + \frac{W_0}{24} \;=\; W_0\cdot(1+\frac{1}{24})\;=\;W_0\cdot\frac{25}{24}$$
Or in other words; We will have $4,\!1\bar{6}$\% additional Wishes .  
\\
For most Travelers this is negligible as the Number of extra Wishes with $90$ Pulls comes down to $3,\!75$ using this Formula.
\\
\\
We can also calculate how many starting Wishes $W_0$ we would need to get to a total amount of $W_T$ Wishes:
$$W_0=\frac{24}{25}\cdot W_T$$
Or in other words; We need $96$\% of our desired Total Wish amount. 
\newpage

\section{References}
\textbf{Genshin Impact} (miHoYo, 2020) \textit{Character Banner Details}
\\
\\
\textbf{Genshin Impact} (miHoYo, 2020) \textit{Pimons Bargain item Shop}

\end{document}
